Assessing environmental and predation effects on Antarctic Krill (*Euphausia superba*) stock productivity: An Integrated Catch-at-Length Model Perspective

### 2025-03-27 MS2_Krill.Rmd
adding stest to MSE

---
title: "Integrated approach to modeling krill population dynamics in the Western Antarctic Peninsula: spatial and ecosystem considerations"
author:
  - Mauricio Mardones^[Universidad de Magallanes, mamardon@umag.cl, Instituto Milenio Base]
  - Lucas Krüger ^[Instituto Antártico Chileno, Instituto Milenio Base]
  - Francisco Santa Cruz ^[Instituto Antártico Chileno, Universidad de Magallanes, Instituto Milenio Base]
  - César Cárdenas^[Instituto Antártico Chileno, Instituto Milenio Base]
  - George Watters^[Ecosystem Science Division, Southwest Fisheries Science Center, NOAA, USA]
output:
  bookdown::pdf_document2:
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
csl: apa.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

```{r setup1, echo=FALSE}
rm(list = ls())
knitr::opts_chunk$set(eval=TRUE,
                      echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

```{r message=FALSE, eval=TRUE}
library(here)
library(kableExtra)
library(ggpubr)
library(tibble)
library(readxl)
library(openxlsx)
library(r4ss)
dir1<-here("s1")
```

@@

```{r mainvar, fig.cap="Main variables outputs (Total Biomass, Biomass at 75%, Spawining biomass and Recruit in t) from estimation in s1 model krill in WAP"}
out_s2 <- read_excel("DataKrill.xlsx", 
    sheet = "variable_s2")
out_s2 %>%
  kbl(booktabs = TRUE,
      format = "latex",
    caption = "Main variables outputs from stock asssessment krill in WAP") %>%
  kable_paper("hover", 
              full_width = TRUE)%>%
  kable_styling(latex_options = c("striped",
                                  "condensed"),
                full_width = TRUE,
                font_size=6 )#%>% 
  #pack_rows(index = c("Estimation" = 1,
   #                     "Prediction" = 45))
```

>>>>

---
title: "Assessing environmental and predation effects on Antarctic Krill (*Euphausia superba*) stock productivity: An Integrated Catch-at-Length Model Perspective"
author:
  - Mauricio Mardones^[Universidad de Magallanes, mamardon@umag.cl, Instituto Milenio Base]
  - Erica Jarvis Mason^[Antarctic División NOAA, USA]
  - Andrea Pinones ^[Instituto Antártico Chileno, Instituto Milenio Base]
  - Francisco Santa Cruz ^[Instituto Antártico Chileno, Universidad de Magallanes, Instituto Milenio Base]
  - César Cárdenas^[Instituto Antártico Chileno, Instituto Milenio Base]
output:
  bookdown::word_document2:
    reference_docx: MS2_Krill_template.docx.docx
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
#csl: apa.csl
csl: icesjournal.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

```{r setup1, echo=FALSE}
rm(list = ls())
knitr::opts_chunk$set(eval=FALSE,
                      echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      tidy.opts=list(width.cutoff=50), 
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

```{r message=FALSE, eval=TRUE}
library(here)
library(kableExtra)
library(ggpubr)
library(tibble)
library(readxl)
library(openxlsx)
library(r4ss)
```

Understanding the drivers of krill (*Euphausia superba*) population dynamics is crucial for sustainable management. This study evaluates the impact of environmental variables and predation components on krill productivity, specifically stock-recruitment relationships and other population parameters, in the Western Antarctic Peninsula. Using an integrated Catch-at-Length model, we assess how ecosystem factors influence recruitment, biomass trends, and stock status.  Our results indicate that krill population variables, as well as productivity estimates, tend to be more optimistic in terms of stock status when environmental and predators variables are not considered. This highlights a critical challenge in developing management recommendations and harvest control rules, as ignoring ecosystem influences may lead to overly optimistic assessments of krill stock health.  Our findings emphasize the necessity of incorporating ecosystem variables into population stock assessments process, as neglecting these factors may lead to biased estimations of krill population dynamics. We consider that the use of integrated models, which leverage the extensive population, fisheries, and ecosystem data available through various scientific programs, can provide valuable insights for management aligned with CCAMLR conservation and harvesting objectives.

**Keywords:** Antarctic krill, population dynamics, stock-recruitment, ecosystem variables, Catch-to-Length model, environmental factors, predation, fisheries management.

Antarctic krill (*Euphausia superba*) is a keystone species in the Antarctic ecosystem and represents one of the largest living populations on the planet in terms of biomass (REF). This species is widely distributed across the Antarctic continental shelf; however, its populations are currently concentrated mainly in the Antarctic Peninsula region (REF). This spatial concentration has heightened scientific interest in understanding the population dynamics of krill, both from an ecological perspective—due to its crucial role as a prey species for whales, penguins, and other marine organisms (REF)—and from an economic standpoint, given the commercial fishing pressure exerted on this resource (REF).

Recognizing the ecological and economic importance of krill, the Commission for the Conservation of Antarctic Marine Living Resources (CCAMLR) has prioritized conservation and management strategies aimed at ensuring the sustainability of this resource. The primary objective has been to reconcile commercial exploitation with a precautionary approach that safeguards the ecological community dependent on krill (REF). CCAMLR’s management framework relies on sustainable exploitation recommendations based largely on survey data obtained from acoustic biomass estimation campaigns and fisheries monitoring programs (REF). Over time, these efforts have advanced toward integrating multiple sources of information into assessment models that guide decision-making. One such approach is the use of annual yield models, which recommend catch limits based on predefined exploitation thresholds (REF).

In this study, we integrate multiple sources of biological and fisheries-related data, including estimates of biomass from scientific surveys, fisheries catch data, and biological parameters, to construct a modern stock assessment model that evaluates key population variables and krill productivity. However, contemporary stock assessment models require the incorporation of ecosystem variables—such as environmental conditions and predator-prey interactions—which are essential components of the Antarctic ecosystem and must be considered when modeling krill population dynamics (REF).

To address these challenges, we integrate environmental information that influences krill population dynamics, as well as data on predator species that are affected by krill population variability. We employ an integrated catch-at-length stock synthesis model to compare different scenarios and assess the impact of ecosystem variability on key productivity indicators, such as recruitment and other critical population variables (REF). By incorporating these ecosystem drivers into our stock assessment approach, we aim to enhance our understanding of krill population fluctuations and improve the scientific basis for sustainable management recommendations.

Antarctic krill (*Euphausia superba*) plays a fundamental role in the Southern Ocean ecosystem, linking primary production to higher trophic levels, including marine mammals, seabirds, and fish. Krill populations are subject to complex ecological pressures, including environmental variability (e.g., sea ice extent, temperature fluctuations, and primary productivity) and predation from key species such as penguins. In addition, commercial fisheries target krill, further influencing population dynamics.

Traditional stock assessments primarily rely on fishery-dependent and survey-based data but often overlook ecosystem variables that may significantly impact population structure and productivity. Integrating environmental and biological drivers into stock assessments is essential to improving our understanding of krill dynamics and ensuring robust management strategies.

This study aims to assess the impact of ecosystem variables, particularly environmental conditions and predation pressure from penguins, on krill productivity and population structure. Using an integrated Catch-to-Length model, we evaluate stock-recruitment relationships and other key population parameters to determine how ecosystem drivers shape krill dynamics.

# M&M

#### **2.1. Study Area and Data Sources**  
This study focuses on the Antarctic Peninsula, a region where krill populations exhibit strong variability due to environmental fluctuations and intense predation pressure. Data were obtained from the Commission for the Conservation of Antarctic Marine Living Resources (CCAMLR), including fishery-dependent catch data, scientific surveys, and predator monitoring datasets. Environmental data, such as sea surface temperature (SST), chlorophyll-a concentration, and sea ice extent, were sourced from satellite observations and oceanographic monitoring programs.

#### **2.2. Catch-to-Length Model Implementation**  
We applied an integrated Catch-to-Length model to estimate krill stock-recruitment relationships and population trends. The model links catch-at-length data with growth, mortality, and recruitment processes while incorporating environmental and predation variables. Key model parameters include:

- Growth rates based on length-frequency distributions  
- Natural mortality estimates derived from predator consumption data  
- Stock-recruitment functions incorporating environmental predictors  
- Fishery removals as a function of effort and environmental conditions

#### **2.3. Statistical Analysis and Model Validation**  
Model performance was evaluated through likelihood-based comparisons, sensitivity analyses, and cross-validation against independent survey datasets. We tested multiple scenarios to assess the relative influence of environmental and predation variables on recruitment and biomass dynamics.

---

### **3. Results**  
Our model results indicate that ecosystem variables significantly influence krill productivity and population structure:

1. **Stock-Recruitment Relationship**: Recruitment was positively correlated with sea ice extent and primary productivity, suggesting a strong link between krill reproduction and environmental conditions.  
2. **Predation Impact**: Penguin predation exerted a measurable effect on juvenile krill survival, with increased predation pressure leading to lower recruitment estimates in years with high predator abundance.  
3. **Biomass Trends**: Environmental drivers accounted for a substantial portion of biomass fluctuations, with warm years showing lower krill abundance, likely due to reduced primary productivity.  
4. **Fisheries Interaction**: Years with high krill harvest coincided with lower biomass estimates, highlighting the cumulative impact of both natural and anthropogenic pressures on krill stocks.

---

### **4. Discussion**  
Our findings emphasize the necessity of incorporating ecosystem variables into krill population assessments. The significant influence of environmental variability and predation highlights the limitations of traditional stock assessment models that assume static population processes.

- **Ecosystem-Based Management Implications**: Our study supports the integration of ecosystem-based reference points in krill fishery regulations. By considering environmental and predation effects, management frameworks can better anticipate population fluctuations and minimize risks of overexploitation.  
- **Predator-Krill Interactions**: The observed impact of penguin predation aligns with previous studies that indicate krill availability is a primary driver of penguin reproductive success. Managing krill fisheries in a way that ensures sufficient prey availability for predators is critical for maintaining ecosystem balance.  
- **Climate Change Considerations**: Given the ongoing warming trends in the Antarctic Peninsula, krill populations may face increased environmental stress. Our results suggest that future management strategies should incorporate climate-driven changes in krill habitat suitability.

---

### **5. Conclusion**  
This study demonstrates that incorporating environmental and predation variables into stock assessments significantly improves our understanding of Antarctic krill population dynamics. The integrated Catch-to-Length model provides a robust framework for assessing krill productivity under varying ecosystem conditions. Our results advocate for an ecosystem-based approach to krill fisheries management, ensuring that decision-making processes account for the broader ecological context.

Future research should explore additional ecosystem interactions and refine predictive models to support adaptive management strategies under changing climatic conditions.

---

### **Acknowledgments**  
We thank CCAMLR for providing access to data and acknowledge the support of the scientific community contributing to krill population research.

---

This draft presents a formal scientific structure suitable for submission to a peer-reviewed journal. Let me know if you need modifications or additional details! 🚀

@@

```{r eval=F, mainvar, fig.cap="Main variables outputs (Total Biomass, Biomass at 75%, Spawining biomass and Recruit in t) from estimation in s1 model krill in WAP"}
out_s2 <- read_excel("DataKrill.xlsx", 
    sheet = "variable_s2")
out_s2 %>%
  kbl(booktabs = TRUE,
      format = "latex",
    caption = "Main variables outputs from stock asssessment krill in WAP") %>%
  kable_paper("hover", 
              full_width = TRUE)%>%
  kable_styling(latex_options = c("striped",
                                  "condensed"),
                full_width = TRUE,
                font_size=6 )#%>% 
  #pack_rows(index = c("Estimation" = 1,
   #                     "Prediction" = 45))
```
